---
title: "Week 4 part 1 - CIs & t-tests"
author: "Elena Ortiz"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 1. Confidence intervals 

Default setting is null hypothesis = 0

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```
## 2. T-test (1-sample t-test)

See a claim: mean otter length is 50 inches 

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```
## 3. Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

## END PART 1

## Part 1: Two-sample t-test 

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact","suv"))
```

### Exploratory data visualization 

Exploratory historgrams: 
```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins = 15) +
  facet_wrap(~class) 
```

### Quantile-quantile to explore how close to linear it is
```{r}
ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~class)
```

### Descriptive statistics

Baseline exploration before doing a t-test

You'd want to think about how representative this group is of the population 

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  dplyr::summarize(mean_city = mean(cty),
                   sd_city = sd(cty),
                   n = n())

car_stats
```

### 2-Sample t-test


Create vectors containing observations for each sample (city gas mileage)

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

t.test(x = compact_sample, suv_sample)
```

